### 2020-01-09 tex/ms.tex
GFA k term

>>>>

\section{GFA k term}
The same code used to predict the GFA zeropoint at airmass = 1 can also be used to predict the $k$-term (magnitudes per airmass of atmospheric extinction), which enters into the calculation of transparencies at sky locations away from zenith. We can estimate the $k$-term by simply taking the difference of the GFA zeropoint magnitude predicted for the artificial case of airmass = 0 and the previously predicted GFA zeropoint magnitude for airmass = 1. For the former, we again use the \verb|ci_throughput| code:

\noindent
\verb|calc_ci_zeropoint, /gfa, airmass=0|

This yields an atmosphere-free predicted zeropoint mag of $r$ = 27.140 AB. The $k$-term is therefore 27.140 $-$ 27.026 = 0.114 magnitudes per airmass. This value is quite similar to the $r$ band $k$-term value of 0.1 magnitudes per airmass adopted by the DESI pre-imaging survey codes \verb|mosstat.pro|\footnote{\url{https://desi.lbl.gov/trac/browser/decam/code/observing/trunk/pro/mosstat.pro\#L293}}, \verb|decstat.pro|\footnote{\url{https://desi.lbl.gov/trac/browser/decam/code/observing/trunk/pro/decstat.pro\#L286}} and \verb|bokstat.pro|\footnote{\url{https://desi.lbl.gov/trac/browser/decam/code/observing/trunk/pro/bokstat.pro\#L245}}.
